---
title: "Data Cleaning and Imputation"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Name : Soumyarup Chatterjee
## Registration Number : 19BCE1031

## Name : Aditi Agarwal
## Registration Number : 19BCE1159


## Data Cleaning and Imputation in R for train.csv datast :- 


### 1. To read train.csv :
```{r}
d<-read.csv("cars_true_value.csv")
```

### 2. To choose first 10 row of data for displaying data set before cleaning :
```{r}
old_d<-d
#displaying data set before cleaning(top 7 rows to make it look less clumsy)
print(old_d[1:10,])
```

### 3.Replacing all blank values with NA   :
```{r}
d[d == ""] <- NA
d1<-d
print(head(d,10))
```

### 4. Replacing NA values in yr_mfr column with median value in that column :
```{r}
#To find the number of NA values in this column
print(sum(is.na(d$yr_mfr)))

#replacing NA values in d1 data set with 0 to find median
d1$yr_mfr[which(is.na(d1$yr_mfr))]<-0
d1$yr_mfr <- as.integer(d1$yr_mfr) 
m<-median(d1$yr_mfr)
d$yr_mfr[which(is.na(d$yr_mfr))]<-m
d$yr_mfr[which(is.na(d$yr_mfr))]<-0
d$yr_mfr<- as.integer(d$yr_mfr) 
m<-median(d1$yr_mfr)
#Median yr_mfr value:
print(m)
#replacing the NA value in d data set with median value
d$yr_mfr[which(is.na(d$yr_mfr))]<-m

#check whether NA values are present in this column after data imputation :
print(sum(is.na(d$yr_mfr)))

```

### 5. Replacing NA values in fuel_type with value occuring max times in that column  :
```{r}
#To find the number of NA values in this column
print(sum(is.na(d$fuel_type)))

#To find the value occurring max times in fuel_type column
t <- na.omit(unique(d$fuel_type))
h<-t[which.max(tabulate(match(d$fuel_type, t)))]
#replacing the NA value in d data set with value occurring max times
d$fuel_type[which(is.na(d$fuel_type))]<-h
print(h)

#check whether NA values are present in this column after data imputation :
print(sum(is.na(d$fuel_type)))
```

### 6. Replacing NA values in  kms_run column with median value in that column :
```{r}
#To find the number of NA values in this column
print(sum(is.na(d$kms_run)))

#replacing NA values in d1 data set with 0 to find median
d1$kms_run[which(is.na(d1$kms_run))]<-0
d1$kms_run <- as.integer(d1$kms_run) 
m<-median(d1$kms_run)
d$kms_run[which(is.na(d$kms_run))]<-m
d1$kms_run[which(is.na(d1$kms_run))]<-0
d1$kms_run <- as.integer(d1$kms_run) 
m<-median(d1$kms_run)
#Median kms_run value:
print(m)
#replacing the NA value in d data set with median value
d$kms_run[which(is.na(d$kms_run))]<-m

#check whether NA values are present in this column after data imputation :
print(sum(is.na(d$kms_run)))
```

### 7. Replacing NA values in sale_price column with the respective value broker_quote in that column :
```{r}
#To find the number of NA values in this column
print(sum(is.na(d$sale_price)))

#replacing NA values in data set d with subsequent broker_quote value 
x=which(is.na(d$sale_price))
d$sale_price[x]=d$broker_quote[x]

#check whether NA values are present in this column after data imputation :
print(sum(is.na(d$sale_price)))
```

### 8. Replacing NA values in times_viewed column with median value in that column :
```{r}
#To find the number of NA values in this column
print(sum(is.na(d$times_viewed)))

#replacing NA values in d1 data set with 0 to find median
d1$times_viewed[which(is.na(d1$times_viewed))]<-0
d1$times_viewed <- as.integer(d1$times_viewed) 
m<-median(d1$times_viewed)
d$times_viewed[which(is.na(d$times_viewed))]<-m
d$sale_price[which(is.na(d$sale_price))]<-0
d1$times_viewed<- as.integer(d1$times_viewed) 
m<-median(d1$times_viewed)
#Median times_viewed value:
print(m)
#replacing the NA value in d data set with median value
d$times_viewed[which(is.na(d$times_viewed))]<-m

#check whether NA values are present in this column after data imputation :
print(sum(is.na(d$times_viewed)))

```

### 9. Omitting rows having NA values in body_type column  :
```{r}
#To find the number of NA values in this column
print(sum(is.na(d$body_type)))

t<-d[,c("body_type")]
d<- d[complete.cases(t), ]

#check whether NA values are present in this column after data imputation :
print(sum(is.na(d$body_type)))
```

### 10. Replacing NA values in transmission column with value occuring max times in that column :
```{r}
#To find the number of NA values in this column
print(sum(is.na(d$transmission)))

#To find the value occurring max times in transmission column
y <- na.omit(unique(d$transmission))
h<-y[which.max(tabulate(match(d$transmission, y)))]

#replacing the NA value in d data set with value occurring max times
d$transmission[which(is.na(d$transmission))]<-h
print(h)

#check whether NA values are present in this column after data imputation :
print(sum(is.na(d$transmission)))

```

### 11. Replacing NA values in variant column  :
```{r}
#To find the number of NA values in this column
print(sum(is.na(d$variant)))
#Since there is no Na value so no need of data imputation.
```

### 12. Replacing NA values in assured_buy  column  :
```{r}
#To find the number of NA values in this column
print(sum(is.na(d$assured_buy)))
#Since there is no Na value so no need of data imputation.
```

### 13. Omitting rows having NA values in registered_city column  :
```{r}
#To find the number of NA values in this column
print(sum(is.na(d$registered_city)))

t<-d[,c("registered_city")]
d<- d[complete.cases(t), ]

#check whether NA values are present in this column after data imputation :
print(sum(is.na(d$registered_city)))
```

### 14. Removing NA values in registered_state column  :
```{r}
#To find the number of NA values in this column
print(sum(is.na(d$registered_state)))
#Since there is no Na value so no need of data imputation.

```

### 15. Replacing NA values in is_hot with value occuring max times in that column  :
```{r}
#To find the number of NA values in this column
print(sum(is.na(d$is_hot)))
#To find the value occurring max times in is_hot column
t <- na.omit(unique(d$is_hot))
h<-t[which.max(tabulate(match(d$is_hot, t)))]

#replacing the NA value in d data set with value occurring max times
d$is_hot[which(is.na(d$is_hot))]<-h
print(h)

#check whether NA values are present in this column after data imputation :
print(sum(is.na(d$is_hot)))
```

### 16. Replacing NA values in rto column  :
```{r}
#To find the number of NA values in this column
print(sum(is.na(d$rto)))
#Since there is no Na value so no need of data imputation.
```

### 17. Replacing NA values in source column  :
```{r}
#To find the number of NA values in this column
print(sum(is.na(d$source)))
#To find the value occurring max times in source column
y <- na.omit(unique(d$source))
h<-y[which.max(tabulate(match(d$source, y)))]

#replacing the NA value in d data set with value occurring max times
d$source[which(is.na(d$source))]<-h
print(h)

#check whether NA values are present in this column after data imputation :
print(sum(is.na(d$source)))
```

### 18. Replacing NA values in make column  :
```{r}
#To find the number of NA values in this column
print(sum(is.na(d$make)))
#Since there is no Na value so no need of data imputation.
```

### 19. Replacing NA values in model column  :
```{r}
#To find the number of NA values in this column
print(sum(is.na(d$model)))
#Since there is no Na value so no need of data imputation.
```

### 20. Replacing NA values in car_availability column with value occuring max times in that column :
```{r}
#To find the number of NA values in this column
print(sum(is.na(d$car_availability)))
#To find the value occurring max times in car_availability column
y <- na.omit(unique(d$car_availability))
h<-y[which.max(tabulate(match(d$car_availability, y)))]

#replacing the NA value in d data set with value occurring max times
d$car_availability[which(is.na(d$car_availability))]<-h
print(h)

#check whether NA values are present in this column after data imputation :
print(sum(is.na(d$car_availability)))

```

### 21. Replacing NA values in total_owners column  :
```{r}
#To find the number of NA values in this column
print(sum(is.na(d$total_owners)))
#Since there is no Na value so no need of data imputation.
```

### 22. Replacing NA values in broker_quote column  :
```{r}
#To find the number of NA values in this column
print(sum(is.na(d$broker_quote)))
#Since there is no Na value so no need of data imputation.
```

### 23. Replacing NA values in original_price column :
```{r}
#To find the number of NA values in this column
print(sum(is.na(d$original_price)))

#replacing NA values in d1 data set with 0 to find median
d$original_price[which(is.na(d$original_price))]=d$sale_price[which(is.na(d$original_price))]+100000

d=d[-c(which(d$sale_price>d$original_price)),]

#check whether NA values are present in this column after data imputation :
print(sum(is.na(d$original_price)))

```

### 24. Replacing NA values in car_rating column with value occuring max times in that column :
```{r}
#To find the number of NA values in this column
print(sum(is.na(d$car_rating)))

#To find the value occurring max times in car_rating column
y <- na.omit(unique(d$car_rating))
h<-y[which.max(tabulate(match(d$car_rating, y)))]

#replacing the NA value in d data set with value occurring max times
d$car_rating[which(is.na(d$car_rating))]<-h
print(h)

#check whether NA values are present in this column after data imputation :
print(sum(is.na(d$car_rating)))

```



### 26. Replacing NA values in fitness_certificate with value occuring max times in that column  :
```{r}
#To find the number of NA values in this column
print(sum(is.na(d$fitness_certificate)))

#To find the value occurring max times in fitness_certificate column
t <- na.omit(unique(d$fitness_certificate))
h<-t[which.max(tabulate(match(d$fitness_certificate, t)))]

#replacing the NA value in d data set with value occurring max times
d$fitness_certificate[which(is.na(d$fitness_certificate))]<-h
print(h)

#check whether NA values are present in this column after data imputation :
print(sum(is.na(d$fitness_certificate)))
```

### 27. Replacing NA values in emi_starts_from column  :
```{r}
#To find the number of NA values in this column
print(sum(is.na(d$emi_starts_from)))
#Since there is no Na value so no need of data imputation.
```

### 28. Replacing NA values in booking_down_pymnt column  :
```{r}
#To find the number of NA values in this column
print(sum(is.na(d$booking_down_pymnt)))
#Since there is no Na value so no need of data imputation.
```

### 29. Replacing NA values in reserved column  :
```{r}
#To find the number of NA values in this column
print(sum(is.na(d$reserved)))
#Since there is no Na value so no need of data imputation.
```

### 30. Replacing NA values in warranty_avail column  :
```{r}
#To find the number of NA values in this column
print(sum(is.na(d$warranty_avail)))
#Since there is no Na value so no need of data imputation.
```

### 31.	Store the details in a comma separated values (csv) file. Also suppress the row numbers :
```{r}
print(sum(is.na(d)))
write.csv(d,"cars_true_value_clean.csv",row.names = FALSE )
```