---
title: "Exploratory Data Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Name : Soumyarup Chatterjee
## Registration Number : 19BCE1031

## Name : Aditi Agarwal
## Registration Number : 19BCE1159


## Predictions models in R for cars_feature_new.csv datast :- 


### To read cars_feature_new.csv :
```{r}
library(MASS)
library(dplyr)
library(ggplot2)
library(RColorBrewer)
library(caret)
library(tidyverse)
library(randomForest)
library(rpart)

df<-read.csv("cars_feature_new.csv")
print(head(df))

```

### Predict percent_price of a car using multiple linear regression:
```{r}
set.seed(150)
train_samples <- df$percent_price %>% createDataPartition(p=0.8,list=F)
head(train_samples)
train <- df[train_samples,]
test <- df[-train_samples,]

model=lm(percent_price~.,data = train)
summary(model)

pred_percent_price=model %>% predict(test)

RMSE <- RMSE(pred_percent_price,test$percent_price)
RMSE

R2 <- R2(pred_percent_price,test$percent_price)
R2

## Visualizing the fit of the model
hist(model$residuals)
qqnorm(model$residuals,ylab = "Residuals")
qqline(model$residuals)

```

### Predict percent_price of a car using decision tree regression:
```{r}
set.seed(150)
train_samples <- df$percent_price %>% createDataPartition(p=0.8,list=F)
head(train_samples)
train <- df[train_samples,]
test <- df[-train_samples,]

model <- rpart(percent_price~., method = "anova", data = train)
print(model)

pred_percent_price=predict(model, test, method = "anova")

plot(model, uniform = TRUE,main = "Car Percent Price Decision Tree using Regression")
text(model, use.n = TRUE, cex = .6)

RMSE <- RMSE(pred_percent_price,test$percent_price)
RMSE

R2 <- R2(pred_percent_price,test$percent_price)
R2


```

### Predict percent_price of a car using random forest regression:
```{r}
set.seed(150)
train_samples <- df$percent_price %>% createDataPartition(p=0.8,list=F)
head(train_samples)
train <- df[train_samples,]
test <- df[-train_samples,]


model = randomForest(percent_price~.,data=test,ntree = 500)
pred_percent_price=predict(model,test)

importance(model)
varImpPlot(model)

RMSE <- RMSE(pred_percent_price,test$percent_price)
RMSE

R2 <- R2(pred_percent_price,test$percent_price)
R2

```








